Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-21

### 2016-02-23 ec-2016/source/paper.tex
Update figure: overview.

\usepackage{tikz}
\usetikzlibrary{chains,decorations.pathreplacing}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}

@@

    B/.style = {decorate,
                decoration={brace, amplitude=5pt,
                pre=moveto,pre length=1pt,post=moveto,post length=1pt,
                raise=1mm,
                            #1}, % for mirroring of brace, if necessary
                thick},
    B/.default=mirror, % by default braces are mirrored

@@

\draw[B] ( A-1.north west) -- node[above=1.5mm] {$h$} ( A-1.north east);
\draw[B] ( A-2.north west) -- node[above=1.5mm] {$l_w - 2h$} ( A-2.north east);
\draw[B] ( A-3.north west) -- node[above=1.5mm] {$h$} ( A-3.north east);
\draw[B] ( A-4.north west) -- node[above=1.5mm] {$m - l_w$} ( A-4.north east);

@@

@@

\foreach \i in {$s$,{\ldots}0\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes

@@

\foreach \i in {$s$,{\ldots}1\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes

@@

\foreach \i in {$s$,{\ldots}1\ldots,{\ldots}$\tilde{s}$\ldots,{\ldots}0}% <-- content of nodes

@@

\foreach \i in {$s$,{\ldots}1\ldots,{\ldots}$\tilde{s}$\ldots,$z_{w,D}$}% <-- content of nodes

@@

@@

\foreach \i in {$z_{w,A}$,{\ldots}1\ldots,{\ldots}$\tilde{s}$\ldots,$z_{w,D}$}% <-- content of nodes

@@

\foreach \i in {$z_{w,A}$,$z_{w,B}$,{\ldots}$\tilde{s}$\ldots,$z_{w,D}$}% <-- content of nodes

@@

\foreach \i in {$z_{w,A}$,$z_{w,B}$,$z_{w,C}$,$z_{w,D}$}% <-- content of nodes

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}

@@

@@

\draw[<->] ([yshift=1.5mm] A-1.north east) -- node[above=0.25mm] {$h$} ([yshift=1.5mm] A-1.north west);
\draw[<->] ([yshift=1.5mm] A-2.north east) -- node[above=0.25mm] {$l_w - 2h$} ([yshift=1.5mm] A-2.north west);
\draw[<->] ([yshift=1.5mm] A-3.north east) -- node[above=0.25mm] {$h$} ([yshift=1.5mm] A-3.north west);
\draw[<->] ([yshift=1.5mm] A-4.north east) -- node[above=0.25mm] {$m - l_w$} ([yshift=1.5mm] A-4.north west);

@@

    Y/.style = {rectangle, draw,% styles of nodes in string (chain)
                outer sep=0pt, on chain, thick},

@@

\node[Y] {$s$};
\foreach \i in {{\ldots}0\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes

@@

\foreach \i in {$s$}% <-- content of nodes
\node[Y] {{\ldots}1\ldots};
\foreach \i in {{\ldots}0\ldots,{\ldots}0}% <-- content of nodes

@@

\foreach \i in {$s$,{\ldots}1\ldots}% <-- content of nodes
\node[Y] {$\tilde{s}$};
\foreach \i in {{\ldots}0}% <-- content of nodes

@@

\foreach \i in {$s$,{\ldots}1\ldots,$\tilde{s}$}% <-- content of nodes

@@

\node[Y] {$z_{w,D}$};

@@

\node[Y] {$z_{w,A}$};
\foreach \i in {{\ldots}1\ldots,$\tilde{s}$,$z_{w,D}$}% <-- content of nodes

@@

\foreach \i in {$z_{w,A}$}% <-- content of nodes
\node[Y] {$z_{w,B}$};
\foreach \i in {$\tilde{s}$,$z_{w,D}$}% <-- content of nodes

@@

\foreach \i in {$z_{w,A}$,$z_{w,B}$}% <-- content of nodes
\node[Y] {$z_{w,C}$};
\foreach \i in {$z_{w,D}$}% <-- content of nodes
